---
title: "README"
author: "Steven W. Nydick"
date: "8/27/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is simply a scratch document to get an idea of the web-scraping presentation.

The following packages might be useful:
1. `curl` or `RCurl` (for general network interfaces).
    a. Use `curl` due to its stability, lack of memory leaks, and implementation
       in other packages.
    b. Keep this part **short** and higher-level because other packages that use
       `curl` can mostly be understood without knowing entirely how `curl` works.
       (might be too into the weeds)
2. `httr` (for general `POST`, `GET`, ... requests).
    a. Explain what each of these request objects due and the structure of
       a given request.
    b. Explain (with examples) the `add_headers` function and how headers
       can be added to individual requests.
       
```{r}
library(httr)

# basic with no additional headers
content(GET("http://httpbin.org/headers"))

# adding version header (see help file)
content(GET("http://httpbin.org/headers",
            add_headers(version = version$version.string)))
```

3. `xml2`/`rjson`/`jsonlite` (for data transfer structure).
    a. Briefly explain "XML" and "JSON" formats.
    b. Introduce packages able to process each of these formats.
    c. Indicate that people can look these up on their own time?
4. APIs.
    a. Introduce what APIs are and how to access common APIs.
    b. Demonstrate how to access the Twitter API, including each of the steps
       so that everybody can actually setup their own account (if they want).
    c. Maybe as a backup have our tokens available so that people can access
       our own account?
    d. What if there's no internet?
5. `twitteR` (plus examples).
    a. Introduce the `twitteR` package, what it does, how it works.
    b. Explicitly setup user access.
    c. Provide some examples of accessing different search queries and how
       to put the data into a usable format in R.
6. Putting it all together.
    a. Brief demonstration of accessing the Twitter API via R to answer a
       particular question with sentiment analysis (Tesla?).
    b. Walk through this section quickly, provide the code so that people can
       run through it on their own.
7. Epilogue ...
    a. Provide additional API accessors via R (`acs` for Census data,
       `RGoogleAnalytics`, `Rfacebook`, etc.)
    b. RESTFUL vs SOAP APIs.
    c. Website that publish data in JSON format.
       See [jsonlite-example](https://cran.r-project.org/web/packages/jsonlite/vignettes/json-apis.html).
