---
title: "htmltab - almost doing it manually"
author: "Korn Ferry Institute"
date: "4/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## When an API isn't available

Sometimes an API just isn't available for what we want to do. For example, it'd
be nice if there was an API to pull data from Wikipedia pages, but, alas, no such API exists.
In cases like that, we need to pull the site's HTML and extract the dta within it. 
In cases where the data are in nicely formatted tables, we can offload the hard work to 
a package called `htmltab` which will download a web page's html, look for the tags
indicating a table, and pull data from HTML tables into dataframes. Think of this as an in-between for
using APIs and writing your own web crawler. 


First, load the `htmltab` and `magrittr` packages
```{r}
require(htmltab)
require(magrittr)
```


We'll pul data from url https://en.wikipedia.org/wiki/Forbes_Global_2000 so first, let's create
a variable for the url
```{r}
url      <- "https://en.wikipedia.org/wiki/Forbes_Global_2000"
```

Now, look ath the page and keep a mental note of how many tables there are - you'll
need to specify which table you want to extract by index number (typically in the order they appear),
just be wary that sometimes a table of contents will count as a table! For this example, we'll
take the third table.

```{r}
# There are 7 table tags sets
#  1. 2018 list
#  2. By country
#  3. By industry sector
#  4. 2017 list
#  5. 2016 list
#  6-7? They're hidden and NOT class = wikitable
#       (Forbes magazine lists)

forbes_200_by_sector <- htmltab(doc   = url, which = 3)
head(forbes_200_by_sector)
```

Easy, huh? If you want to see what `htmltab` was targetting:


* Open the Wikipedia page

* Right-click on the table and choose `inspect element`

* In the inspect element pane, you can see the page's content alongside the HTML
that creates it. You'll see tages that look like: `<table class = "...">` in which 
everything related to the table is nested, along with 
`<tbody>` containing the body of the table and and the rows as `<tr>` tags.


In the next section, we'll show you how to create a web-crawler from scratch by 
pulling out specific parts of a page's HTML structure, even when the information we want isn't 
stored in a table object. 