---
title: "APIs"
author: "Korn Ferry Institute"
date: "3/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Simple APIs

We'll start with using an **API** or **A**pplication **P**rogram **I**nterface. 

An API is effectivelly a toolkit that someone makes to help other people work with 
software they've made. Put simply, an API (hopefully) takes out the mess and headaches
of trying to get two programs to work together nicely. Companies like Microsoft, 
Twitter, Amazon Web Services, Facebook, and Linkedin also provide APIs to help people 
nterface with their online services in a controlled way.

In this tutorial, we will use Linkedin's API because it is quick and easy to get started with. 
Before we can use Linkedin's API, we need to get authentication credentials (similar to a username
and password) which Linkedin will check when we use their API to request data. 

The following steps will et you started:

* Log into your linkedin account and go to https://www.linkedin.com/developers/ 
* Press **Create App**
* Fill out the required information
* Then go to the **Auth** page
* And copy down your **Client ID** and **Client Secret** in your Rscript
* You can also save time later on by putting http://localhost:1410/ in your redirect URL

```{r, echo=FALSE, results='hide',message=FALSE}
client_id     <- "86uxrl12ju03xl"
client_secret <- "cXD7SlUKVZPGuIum"
```

```{r, eval=FALSE} 
client_id     <- "xXuseYourIDXx"
client_secret <- "123useYouOne321"

```

Now you're ready to use your new API key. 

First, you'll need the package `RLinkedin` 
which is designed to make API calls easy. We'll also get `magrittr` because `magrittr` 
is nice. Then use `RLinkedin` to create what's called an oAuth object - a glorified
authorization string. When you create it, your browser will ask you to authorizer the
access request for your app

**Follow the prompts when you first authenticate!**
```{r, message=FALSE}
require(Rlinkedin)
require(magrittr)
```
```{r}
auth <- inOAuth(application_name = "fairly_arbitrary_name",
                consumer_key     = client_id,
                consumer_secret  = client_secret)

```

Now we can do everything that Linkedin will let us do with their free API! Are you ready?
Here goes! 

**Note: at the time of writing, `RLinkedin` appears to be broken so this may not work**
````{r, eval = FALSE}
# get your own profile information. 
my_data <- getProfile(auth) %>% as.data.frame()
my_data
```

...And that's it. Linkedin restricted what people can do with their free API. 
Now you can only get your own profile information. 
That's actually the biggest drawback of using an API - you're limited to the tools
other people have made. 

Next up, we'll start the process of breaking free of API calls like this one! 

